---
title: "Organoid_figures_plotting"
author: "HuangFei"
date: "2021/1/22"
output: html_document
---

## load dependence
```{r,warning=FALSE}
need_pkgs <- c('Seurat','cowplot', 'slingshot','ggpubr',
               'data.table', 'reticulate','ggplot2')

for(i in need_pkgs){
  #if(!require(i, character.only = T)) {
   # install.packages(i)
    require(i, quietly = T, character.only = T)
   # } 
}
```

```{r,echo=FALSE}
library(ggplot2)
my_theme <- theme(plot.title = element_text(hjust = 0.5, size = 20),
                  #legend.position = 'right',
                  legend.title =element_text(size=15),
                  legend.text = element_text(size=15),
                  axis.text.x = element_text(size=15),
                  axis.title.x = element_text(size=15),
                  axis.title.y = element_text(size=15),
                  axis.text.y  = element_text(size=15),
                  panel.border = element_blank(),
                  axis.line.x = element_line(size=0.25, color="black"),
                  axis.line.y = element_line(size=0.25, color="black"),
                  panel.grid.minor.x = element_blank(), panel.grid.minor.y = element_blank(),
                  panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
                  panel.background = element_rect(fill='white'),
                  legend.key=element_blank(),
                  strip.text.x = element_text(size=15),
                  strip.text.y = element_text(size=15),
                  strip.background = element_rect(colour = 'white', fill = 'white'))
```

## FigS2: cortical markers
```{r,fig.width=8,fig.height=4.5}
SC_organoid = readRDS('~/Project/Organoid/result/rdata/IVD_organoid_200_min_gene_20MT_Seurat_obj.rds')

cortical = c('CUX1','BCL11B','FOXP2','EMX1','AUTS2','TBR1')

FeaturePlot(SC_organoid, cortical,cols = c("lightgrey",'#FF4500'),ncol = 3)

pdf('~/Project/Organoid/figure/In_paper/Supply_Fig/FigS2_Cortical_markers_in_IVD.pdf',8,4.5)
FeaturePlot(SC_organoid, cortical,cols = c("lightgrey",'#FF4500'),ncol = 3)
dev.off()
```



## FigS4: Integration analysis of IVD-organoids and choroid plexus organoids.

## Load the integration data of IVD and ChP-organoids (Pellegrini-2020-Science)
```{r}
load('~/Project/Organoid/result/Integration/Integrate_IVD_and_ChP_organoids.RData')
DefaultAssay(organoid.integrated) <- 'RNA'
Imeta <- organoid.integrated@meta.data
```

### UMAP
```{r,fig.width=10,fig.height=4}
tsne1 <- DimPlot(organoid.integrated[,], group.by = c( "orig.ident"),label = T, reduction = 'tsne')+my_theme
tsne2 <- DimPlot(organoid.integrated[,], group.by = c( "CellType"),label = T, reduction = 'tsne')+my_theme

tsne<-plot_grid(tsne1, tsne2,rel_widths = c(1,0.95))
tsne
```


```{r}
load('~/Project/Organoid/result/rdata/Summarize_IVD_and_ChP_organoid_matrix.RData')
colnames(IVD_aver)
colnames(ChP_aver) = paste('Organoid', colnames(ChP_aver))

#mat_aver = cbind(IVD_aver[,c(1)],ChP_aver[,c(3,4)])
mat_aver = cbind(IVD_aver[,-c(3,5,6)],ChP_aver[,])
head(mat_aver)
```


### correlation
```{r,fig.width=5.5,fig.height=4.5}
library(RColorBrewer)
library(pheatmap)
aver_cor = cor(mat_aver)
dim(aver_cor)


pheatmap::pheatmap(aver_cor)

#pdf('~/Project/Organoid/figure/to_pub/fig4/choroid_plexus/Correlation_heatmap_between_IVD_and_ChP_organoids.pdf',5.5,4.5)
corH <- pheatmap(aver_cor,fontsize_col = 13,fontsize_row = 13,
                   fontsize = 11,angle_col = 315,
                   color = colorRampPalette(rev(brewer.pal(n = 7, name ="RdBu")))(50))

#dev.off()
```

### PCA
```{r,fig.width=5.6,fig.height=3.5}
mat_aver = cbind(IVD_aver[,-c(3,5,6)],ChP_aver[,])
head(mat_aver)
vars = apply(mat_aver,1,sd)
summary(vars)
vars = sort(vars,decreasing = T)

aver_pca = prcomp(t(mat_aver[names(vars)[1:500],]),
                  center = T)

pr_var <- (aver_pca$sdev)^2
pr_var

summary(aver_pca)

pca_df = as.data.frame(aver_pca$x[,1:2])
pca_df = tibble::rownames_to_column(pca_df, var = 'ID')
pca_df


pcp = ggplot(pca_df, aes(PC1,PC2,col=ID))+geom_point(size=5)+my_theme+
  labs(x='PC1 (36%)', y = 'PC2 (33%)')+ ###stat_ellipse()+ too few points to calculate ellipse
  theme(legend.position = 'right',legend.title = element_blank())
pcp

```

### PCA
```{r,fig.width=5.6,fig.height=3.5}
mat_aver = cbind(IVD_aver[,1],ChP_aver[,])
head(mat_aver)
colnames(mat_aver)[1] = 'IVD ChP'

vars = apply(mat_aver,1,sd)
summary(vars)
vars = sort(vars,decreasing = T)

aver_pca = prcomp(t(mat_aver[names(vars)[1:500],]),
                  center = T)

pr_var <- (aver_pca$sdev)^2
pr_var

summary(aver_pca)

pca_df = as.data.frame(aver_pca$x[,1:2])
pca_df = tibble::rownames_to_column(pca_df, var = 'ID')
pca_df


pcp = ggplot(pca_df, aes(PC1,PC2,col=ID))+geom_point(size=5)+my_theme+
  labs(x='PC1 (55%)', y = 'PC2 (31%)')+ ###stat_ellipse()+ too few points to calculate ellipse
  theme(legend.position = 'right',legend.title = element_blank(),legend.text = element_text(size=15))
pcp

pdf('~/Project/Organoid/figure/to_pub/fig4/PCA_plot_between_IVD_ChP_and_ChP_organoids.pdf',5,3)
pcp
dev.off()
```

 


## plot significant ChP markers in IVD-organoids
```{r}
SC_organoid = readRDS('~/Project/Organoid/result/rdata/IVD_organoid_200_min_gene_20MT_Seurat_obj.rds')
exprMatrix = as.matrix(SC_organoid@assays$RNA@data)

cellsUMAP = Embeddings(object = SC_organoid, reduction = "umap")

cellsTsne = Embeddings(object = SC_organoid, reduction = "tsne")

cellsReduction = as.data.frame(cbind(cellsUMAP, cellsTsne))
cellsReduction$SampleID = rownames(cellsReduction)

meta = SC_organoid@meta.data

meta = cbind(meta,cellsReduction)
head(meta)
setDT(meta)
```

```{r,fig.width=7.5,fig.height=3.5,warning=FALSE,message=FALSE}
setDT(meta)


gene = 'EMX2'
cellsReduction$expr = exprMatrix[gene,rownames(cellsReduction)]

target = exprMatrix[gene, ]
target = sort(target)

EMX2 = ggplot(cellsReduction[names(target),],
              aes(x=UMAP_1,y=UMAP_2,col=expr))+#xlim(c(-10,7.5))+
    geom_point(size=1)+scale_color_gradient(low = 'lightgrey', high = '#FF4500') +
    my_theme+ labs(title = 'EMX2', x = 'UMAP1', y = 'UMAP2')+theme(legend.position = 'none')


gene = 'SIX3'
cellsReduction$expr = exprMatrix[gene,rownames(cellsReduction)]

target = exprMatrix[gene, ]
target = sort(target)

SIX3 = ggplot(cellsReduction[names(target),],
              aes(x=UMAP_1,y=UMAP_2,col=expr))+ #xlim(c(-10,7.5))+
    geom_point(size=1)+scale_color_gradient(low = 'lightgrey', high = '#FF4500') +
    my_theme+ labs(title = 'SIX3', x = 'UMAP1', y = 'UMAP2')+theme(legend.position = 'none')



gene = 'EN2'
cellsReduction$expr = exprMatrix[gene,rownames(cellsReduction)]

target = exprMatrix[gene, ]
target = sort(target)

EN2 = ggplot(cellsReduction[names(target),],
              aes(x=UMAP_1,y=UMAP_2,col=expr))+#xlim(c(-10,7.5))+
    geom_point(size=1)+scale_color_gradient(low = 'lightgrey', high = '#FF4500') +
    my_theme+ labs(title = 'EN2', x = 'UMAP1', y = 'UMAP2')+theme(legend.position = 'none')


gene = 'MEIS1'
cellsReduction$expr = exprMatrix[gene,rownames(cellsReduction)]

target = exprMatrix[gene, ]
target = sort(target)

MEIS1 = ggplot(cellsReduction[names(target),],
              aes(x=UMAP_1,y=UMAP_2,col=expr))+#xlim(c(-10,7.5))+
    geom_point(size=1)+scale_color_gradient(low = 'lightgrey', high = '#FF4500') +
    my_theme+ labs(title = 'MEIS1', x = 'UMAP1', y = 'UMAP2')+theme(legend.position = 'none')

```


```{r,fig.width=5,fig.height=5}
region<-plot_grid(EMX2, SIX3, EN2, MEIS1, ncol = 2)
region
```


```{r,fig.width=12,fig.height=10}
S4<-plot_grid(tsne1,tsne2,corH$gtable,region,
          labels = c('A','B','C','D'), label_size = 25, rel_heights = c(0.7,1))
S4

pdf('~/Project/Organoid/figure/In_paper/Supply_Fig/FigS4_integration_of_IVD_and_ChP_organoids.pdf',12,10)
S4
dev.off()

```


## FigS5: Integration analysis of IVD-organoids, hCOs and vhCOs.
```{r}
load('~/Project/Organoid/result/rdata/Integrate_IVD_and_Cakir_vhCO_Seurat_obj.RData')
```

### plot integrated organoids
```{r}
Imeta = organoid.integrated@meta.data
table(Imeta$CellType)
Imeta = Imeta[grep('Out|Unk|ME|UPRC',Imeta$CellType,invert = T),]

organoid.integrated = organoid.integrated[,rownames(Imeta)]
organoid.integrated@meta.data = Imeta

celltype = DimPlot(organoid.integrated,group.by = c('CellType'))+my_theme
dataset = DimPlot(organoid.integrated,group.by = c('DataSet'))+my_theme

plot_grid(dataset,celltype,rel_widths = c(1,0.95))
```


### plot ChP cells
```{r,fig.width=9,fig.height=4}
Imeta = organoid.integrated@meta.data
head(Imeta)
#Imeta[grep('hCO',Imeta$DataSet),]$DataSet = paste(Imeta[grep('hCO',Imeta$DataSet),]$DataSet,'(Cakir)')
ChP_cells = Imeta[Imeta$integrated_snn_res.0.3==2&Imeta$CellType%in%c('Ependyma','CBC'),]
table(ChP_cells$DataSet)
table(ChP_cells$CellType)
ChP = organoid.integrated[,rownames(ChP_cells)]
CPcelltype = DimPlot(ChP,group.by = c('CellType'))+ylim(c(-11,-1))+my_theme
CPdataset = DimPlot(ChP,group.by = c('DataSet'))+ylim(c(-11,-1))+my_theme
plot_grid(CPdataset,CPcelltype,rel_widths = c(1,0.95))
```

### secretion proteins
```{r,fig.height=8.7,fig.width=9}
ChP_cells = ChP@meta.data
table(ChP_cells$DataSet)
CP_mat = ChP@assays$RNA@data

secrected_proteins = c('AQP1','APOE','APOD','IGFBP7','CA2','CA12','PARK7','SERPINF1','SLC46A1','SLC23A2')

CP_melt = reshape2::melt(as.matrix(CP_mat[rownames(CP_mat)%in%c(secrected_proteins),]))
colnames(CP_melt) = c('gene_name','cellID','Expression')
setDT(CP_melt)
CP_melt$DataSet = 'IVD-organoids'
CP_melt[cellID%in%rownames(ChP_cells[ChP_cells$DataSet=='vhCO',])]$DataSet = 'vhCO (Cakir)'
CP_melt[cellID%in%rownames(ChP_cells[ChP_cells$DataSet=='hCO',])]$DataSet = 'hCO (Cakir)'
CP_melt = CP_melt[grep('vhCO',DataSet,invert = T)]

comparison_list = list(c('hCO (Cakir)','IVD-organoids'))

plot.colors = pal_jama()(6)[c(4,5)]

CP_melt = CP_melt[order(gene_name)]

CP_melt[,DataSet:=factor(DataSet,levels = c('hCO (Cakir)','IVD-organoids'))]

toplot = CP_melt[gene_name%in%c('APOD','CA2','CA12','IGFBP7','SERPINF1','PARK7')]
toplot[,gene_name:=factor(gene_name,levels = c('APOD','CA2','CA12','IGFBP7','SERPINF1','PARK7'))]

p1 = ggpubr::ggviolin(toplot,
                      x = 'DataSet', y = 'Expression',
                 fill = 'DataSet', ylab = 'Relative expression',
                 trim = T, title = '',xlab = '')+
geom_point(size=1,position="jitter", alpha=.7)+
 stat_compare_means(comparisons = comparison_list,
                   label = 'p.signif') + 
  facet_wrap(~gene_name,ncol = 3)+
  my_theme + theme(legend.position = 'none',axis.text.x = element_text(size=16,angle = 40,vjust = 0.9,hjust = 0.9)) + 
  scale_fill_manual(values = plot.colors)

p1

#pdf('~/Project/Organoid/figure/to_pub/fig4/choroid_plexus/ChP_protein/Comparison_of_secrected_proteins_between_IVD_and_Cakir_hCOs.pdf',12,8.7)
#p1
#dev.off()
```


## plot significant ChP markers in IVD-organoids
```{r}
exprMatrix = as.matrix(SC_organoid@assays$RNA@data)

cellsUMAP = Embeddings(object = SC_organoid, reduction = "umap")

cellsTsne = Embeddings(object = SC_organoid, reduction = "tsne")

cellsReduction = as.data.frame(cbind(cellsUMAP, cellsTsne))
cellsReduction$SampleID = rownames(cellsReduction)

meta = SC_organoid@meta.data

meta = cbind(meta,cellsReduction)
head(meta)
setDT(meta)
```

```{r,fig.width=7.5,fig.height=3.5,warning=FALSE,message=FALSE}
setDT(meta)
target_cells = meta[RNA_snn_res.0.2%in%c(0)&CellType%in%c('Ependymal')&UMAP_2>2]$cellID

gene = 'CA2'
cellsReduction$expr = exprMatrix[gene,rownames(cellsReduction)]

target = exprMatrix[gene, target_cells]
target = sort(target)

non_target = exprMatrix[gene, !colnames(exprMatrix)%in%target_cells]
non_target = sort(non_target, decreasing = T)

tmp1 = ggplot(cellsReduction[c(names(non_target),names(target)),],
              aes(x=UMAP_1,y=UMAP_2,col=expr))+#xlim(c(-10,7.5))+
    geom_point(size=1)+scale_color_gradient(low = 'lightgrey', high = '#FF4500') +
    my_theme+ labs(title = 'CA2', x = 'UMAP1', y = 'UMAP2')+theme(legend.position = 'none')
CA2 = tmp1

gene = 'CA12'
cellsReduction$expr = exprMatrix[gene,rownames(cellsReduction)]

target = exprMatrix[gene, target_cells]
target = sort(target)

non_target = exprMatrix[gene, !colnames(exprMatrix)%in%target_cells]
non_target = sort(non_target, decreasing = T)

tmp2 = ggplot(cellsReduction[c(names(non_target),names(target)),],
              aes(x=UMAP_1,y=UMAP_2,col=expr))+ #xlim(c(-10,7.5))+
    geom_point(size=1)+scale_color_gradient(low = 'lightgrey', high = '#FF4500') +
    my_theme+ labs(title = 'CA12', x = 'UMAP1', y = 'UMAP2')+theme(legend.position = 'none')
CA12 = tmp2


plot_grid(tmp1, tmp2,ncol = 2)

#pdf('~/Project/Organoid/figure/to_pub/fig2/BRC_markers_UMAP.pdf',6,3.5)
plot_grid(tmp1, tmp2, ncol = 2)
#dev.off()



gene = 'APOD'
cellsReduction$expr = exprMatrix[gene,rownames(cellsReduction)]

target = exprMatrix[gene, target_cells]
target = sort(target)

non_target = exprMatrix[gene, !colnames(exprMatrix)%in%target_cells]
non_target = sort(non_target, decreasing = T)

tmp5 = ggplot(cellsReduction[c(names(non_target),names(target)),],
              aes(x=UMAP_1,y=UMAP_2,col=expr))+#xlim(c(-10,7.5))+
    geom_point(size=1)+scale_color_gradient(low = 'lightgrey', high = '#FF4500') +
    my_theme+ labs(title = 'APOD', x = 'UMAP1', y = 'UMAP2')+theme(legend.position = 'none')
APOD = tmp5


target_cells = meta[RNA_snn_res.0.2%in%c(0,4,6)&CellType%in%c('Ependymal','BRC')][UMAP_2>2|UMAP_2<(-2)]$cellID
gene = 'IGFBP7'
cellsReduction$expr = exprMatrix[gene,rownames(cellsReduction)]

target = exprMatrix[gene, target_cells]
target = sort(target)

non_target = exprMatrix[gene, !colnames(exprMatrix)%in%target_cells]
non_target = sort(non_target, decreasing = T)

IGFBP7 = ggplot(cellsReduction[c(names(non_target),names(target)),],
              aes(x=UMAP_1,y=UMAP_2,col=expr))+#xlim(c(-10,7.5))+
    geom_point(size=1)+scale_color_gradient(low = 'lightgrey', high = '#FF4500') +
    my_theme+ labs(title = 'IGFBP7', x = 'UMAP1', y = 'UMAP2')+theme(legend.position = 'none')


gene = 'PARK7'
cellsReduction$expr = exprMatrix[gene,rownames(cellsReduction)]

target = exprMatrix[gene, target_cells]
target = sort(target)

non_target = exprMatrix[gene, !colnames(exprMatrix)%in%target_cells]
non_target = sort(non_target, decreasing = T)

PARK7 = ggplot(cellsReduction[c(names(non_target),names(target)),],
              aes(x=UMAP_1,y=UMAP_2,col=expr))+#xlim(c(-10,7.5))+
    geom_point(size=1)+scale_color_gradient(low = 'lightgrey', high = '#FF4500') +
    my_theme+ labs(title = 'PARK7', x = 'UMAP1', y = 'UMAP2')+theme(legend.position = 'none')



gene = 'SERPINF1'
cellsReduction$expr = exprMatrix[gene,rownames(cellsReduction)]

target = exprMatrix[gene, target_cells]
target = sort(target)

non_target = exprMatrix[gene, !colnames(exprMatrix)%in%target_cells]
non_target = sort(non_target, decreasing = T)

SERPINF1 = ggplot(cellsReduction[c(names(non_target),names(target)),],
              aes(x=UMAP_1,y=UMAP_2,col=expr))+ #xlim(c(-10,7.5))+
    geom_point(size=1)+scale_color_gradient(low = 'lightgrey', high = '#FF4500') +
    my_theme+ labs(title = 'SERPINF1', x = 'UMAP1', y = 'UMAP2')+theme(legend.position = 'none')
```
```{r,fig.width=7.5,fig.height=5}
plot_grid(APOD,CA2,CA12,IGFBP7,PARK7,SERPINF1,ncol = 3)

fd = plot_grid(APOD,CA2,CA12,IGFBP7,PARK7,SERPINF1,ncol = 3)

pdf('~/Project/Organoid/figure/In_paper/Supply_Fig/FigS3_ChP_proteins_in_IVD.pdf',7,4.8)
fd
dev.off()
```


```{r,fig.width=12,fig.height=18}


fa = plot_grid(dataset, celltype, ncol = 2)
fb = plot_grid(CPdataset, CPcelltype, ncol = 2, rel_widths = c(1,0.95))

S3 = plot_grid(fa,fb,p1, ncol = 1,
               rel_heights = c(0.5,0.5,1),
               labels = c('A','B','C'), label_size = 25)
S3

pdf('~/Project/Organoid/figure/In_paper/Supply_Fig/FigS5_integration_of_IVD_and_hCOs.pdf',12,17)
S3
dev.off()
```



## FigS6: Comparison of apoptosis and cellular stress gene signatures between IVD-organoids and in vitro organoids.
```{r}
load('~/Project/Organoid/result/rdata/Mutiple_organoid_EN_and_RGC_matrix.RData')
SC_organoid = readRDS('~/Project/Organoid/result/rdata/IVD_organoid_200_min_gene_20MT_Seurat_obj.rds')
meta = SC_organoid@meta.data

RG_cells = rownames(meta[grep('RG|AS',meta$CellType),])
IVD.RG_mat = SC_organoid[,RG_cells]@assays$RNA@data
dim(IVD.RG_mat)

EN_cells = rownames(meta[grep('Neuron',meta$CellType),])
IVD.EN_mat = SC_organoid[,EN_cells]@assays$RNA@data
dim(IVD.EN_mat)

plot.colors = pal_jama()(5)[-1]
```

### comparison of Dorsomedial telencephalon, midbrain and hippocampus markers
```{r,fig.width=10,fig.height=5.5}
common_genes = Reduce(intersect, list(rownames(Bhaduri.EN_mat),
                                      rownames(IVD.EN_mat),
                                      rownames(Giandomenico.EN_mat),
                                      rownames(Velasco.EN_mat)))

EN_mat = Reduce(cbind, list(Bhaduri.EN_mat[common_genes,],
                            IVD.EN_mat[common_genes,],
                            Giandomenico.EN_mat[common_genes,],
                            Velasco.EN_mat[common_genes,]))


EN_melt = reshape2::melt(as.matrix(EN_mat[rownames(EN_mat)%in% c('PGK1','ARCN1','GORASP2'),]))
setDT(EN_melt)
colnames(EN_melt) = c('gene_name','cellID','Expression')
EN_melt$DataSet = 'IVD-organoids'
EN_melt[cellID%in%colnames(Bhaduri.EN_mat)]$DataSet = 'Bhaduri et al.'
EN_melt[cellID%in%colnames(Velasco.EN_mat)]$DataSet = 'Velasco et al.'
EN_melt[cellID%in%colnames(Giandomenico.EN_mat)]$DataSet = 'Giandomenico et al.'

EN_melt[,DataSet:=factor(DataSet, levels = c('Bhaduri et al.',
                                               'Giandomenico et al.','Velasco et al.','IVD-organoids'))]


comparison_list2 = list()
for(i in unique(EN_melt$DataSet)[-2]){
  comparison_list2[[i]] = c('IVD-organoids',i)
}


EN_melt[,gene_name:=factor(gene_name,levels = c('PGK1','ARCN1','GORASP2'))]
EN_melt = EN_melt[order(gene_name)]


PhCO <- ggpubr::ggviolin(EN_melt,
                      x = 'DataSet', y = 'Expression',
                 fill = 'DataSet', ylab = 'Relative expression',
                 trim = T, title = '',xlab = '')+
  geom_point(size=0.1,position="jitter", alpha=.75)+
 stat_compare_means(comparisons = comparison_list2,
                                label = 'p.signif') + 
  facet_wrap(~gene_name,ncol = 3)+ scale_fill_manual(values = pal_jama()(5)[-1])+
  my_theme + theme(legend.position = 'none',axis.text.x = element_text(size=16,angle = 40,vjust = 0.9,hjust = 0.9))
```


```{r,fig.width=14,fig.height=12}
plot.colors = pal_jama()(6)[c(1:3,6,4,5)][c(4,6)]

down_ChP = plot_grid(apoptosis,Hypoxia,Glycolysis,ER_stress,ncol = 2)
down_ChP

tmp <- plot_grid(down_ChP, p2, ncol = 2)
tmp

tmp <- plot_grid(PhCO,p2,ncol = 1,labels = c('A','B'), label_size = 25)

S6 = plot_grid(tmp, down_ChP, ncol = 2, rel_widths = c(1,0.7),
               labels = c('','C'),label_size = 25)
S6

pdf('~/Project/Organoid/figure/In_paper/Supply_Fig/FigS6_comparison_of_cell_stress_signature.pdf',14,11)
S6
dev.off()
```

## FigS7. Subtype analysis of Choroid plexus in IVD-organoids. There is some problems when combining FeaturePlot of Seurat
```{r,fig.width=14,fig.height=10}
clu_tsne = TSNEPlot(ChP, label = T)


S7_1 = plot_grid(clu_tsne, go_bar, ncol = 1, labels = c('A','C'), label_size = 25)
S7_1

clu_dot <- DotPlot(ChP, features = unique(c('CXCL14','CLDN5',Dark_markers[-c(4,6,8,11)][c(1,3:5)],c('MT-ATP6','MT-CO1','MT-ND1'),
                          Light_markers[-c(5,10:13)][c(1,5:8)],c('RSPH9','NPM1','CDK2AP2'))))+
  labs(x = '', y = 'Cluster')+ my_theme + 
  annotate('rect',xmin = 0, xmax = 8, ymax = -0.2,ymin=-0.3, fill = hue_pal()(2)[1])+
  annotate('text',x=3,y = -0.1,label='Dark cells',size = 7) + 
  annotate('rect',xmin = 8, xmax = 17, ymax = -0.2,ymin=-0.3, fill = hue_pal()(2)[2])+
    annotate('text',x=11,y = -0.1,label='Light cells',size=7)+
  theme(axis.text.x = element_text(size=15,angle = 45,vjust = 0.99,hjust = 0.99))


S7_2 =  plot_grid(tsne_dot,clu_dot, ncol = 1, labels = c('B','D'), label_size = 25)

S7 = plot_grid(S7_1,S7_2,ncol = 2, rel_widths = c(0.9,1))
S7
```

```{r}
pdf('~/Project/Organoid/figure/In_paper/Supply_Fig/FigS7_IVD_ChP_subtype_analysis.pdf',14,10)
S7
dev.off()
```
